\subsection*{Twitter}

The team\textquotesingle{}s main social media account is on Twitter\+: \href{https://twitter.com/beeSafe_uofg/}{\tt https\+://twitter.\+com/bee\+Safe\+\_\+uofg/} ~\newline
 Twitter was agreed on as a suitable choice, as its basis of short, frequent message sharing was in line with our marketing strategy, sharing small, regular updates of our project progress with the world. ~\newline
 With none of the team members active social media and Twitter users, this was a new skill we learned during the project. Having been retweeted by the manufacturer of our communications module, u-\/blox, we gained moderate traction on Twitter sharing milestones of our project, both positive and negative. At the submission of the project, we have almost 50 followers, and have followed over a hundred accounts -\/ these include other teams, university contacts and industry players. The social media marketing skills gained helped us learn how small, open-\/source or startup projects can start establishing a presence in a very competitive market by focusing on building a supportive community via social media.

\subsection*{Instagram}

The team initially had an Instagram page, however due to the nature of Instagram, the project did not gather sufficient traction. This led to the decision to deactivate our Instagram account, and instead focus on Twitter marketing.

\subsection*{Contacts}

During the initial design process, the team recognised there are two key restrictions to our project\+: the permitted project budget, and the physical dimensions of the hardware. It was clear from the very beginning that we needed a communications module that uses a mobile network that is strong enough in the Glasgow area, and an antenna that does not make the hardware too clunky. To tackle this, and to avoid having to make too big compromises, the team actively reached out to manufacturers of both the communications modules and antennas to enquire about receiving free test samples, introducing ourselves and the project background. However, there was a general trend of slow responses observed. By the time the team received a response that would have allowed for a partnership to be set up, all hardware components have been ordered, and the initial works on the P\+CB have begun. All in all, this taught us about the willingness of companies to provide help to students, and while we were positively surprised about the responses received, we learned a lesson about the communication timescales of medium to large companies and got a taster to an entrepreneurial mindset. 